Tidal field anisotropy as a tracer of cosmic voids

### 2015-02-12 cosmic_voids.tex
reordenando las seccion de resultados

We use the Bolshoi simulation to test the method describe in the
paper. 
This simulation follows the non-linear evolution of a dark
matter density field on a cubic volume of  size $250$\hMpc\ sampled
with $2048^3$ particles. 
The cosmological parameters in the simulation are $\Omega_{\rm m}=0.27$,  $\Omega_{\Lambda}  =0.73$, $h=0.70$,
$n=0.95$ and $\sigma_{8}=0.82$ for the matter density,   cosmological
constant, dimensionless Hubble parameter, spectral index of
primordial density perturbations and normalization for the power
spectrum, respectively. 
This values are consistent with the seventh year of data of the Wilkinson 
Microwave Anisotropy Probe (WMAP) \citep{Jarosik11}. 
For more detailed  technical information about the simulation, see
\citet{Klypin11}.

We find the cosmic web we estimate first the density and velocity
fields using a  \textit{cloud-in-cell} (\texttt{CIC}) algorithm onto a grid of $256^3$ 
cells, corresponding to a spatial resolution of $0.98$\hMpc\ per cell
side.  
These fields are smoothed with a gaussian filter with a width of
$\sigma=0.98$\hMpc.
We compute the tidal and shear tensors through finite-differences and
Finally, the eigenvalues and eigenvectors of the tensor are
obtained for each grid cell.
The data we use here is publicly available through the MultiDark
database \url{http://www.multidark.org/MultiDark/} which is described
in \citet{Riebe11}.

@@

%-------------------------------------------------------------------------
\subsection{Enclosed mass}
\label{subsec:enclosedmass}
%-------------------------------------------------------------------------

When we analyse individual density profiles of voids (see left panels of
Fig. \ref{fig:RhoVel}), they seem to be distributed in two different 
families, differentiated by the presence or absence of a compensation 
ridge (e.g. see also Fig. 14 of \citet{Colberg05}). In order to 
discriminate each void in one of the families, we propose the compensation 
index $\mathcal{C}$, which is defined as the mass of a void enclosed in a 
spherical volume of radius $R$ and normalized by the mass of the same 
volume as assuming the mean background density instead

@@

Since the shape of the voids exhibit a wide range of geometries, a common 
way to represent their size is through the equivalent spherical radius or
effective radius, defined as $\reff = [3/(4\pi)V]^{1/3}$, with $V$ the 
total volume of the void. As mentioned before, we applied a threshold merger
in order to avoid void hierarchization, what means we are working with the
top hierarchy of voids. We limit our findings to voids with effective radius
greater than the smoothing length of the density field, i.e. $\sim 1$\hMpc. 
Below that scale numerical resolution effects becomes important. We find a
volume filling fraction of voids of $54.88\%$ of the total volume of the 
simulation for the FA-T-web and $47.06\%$ for the FA-Vweb.

In Fig. \ref{fig:volume_function} we show the void size distributions
for both schemes and for the overall distribution of voids as well as for 
overcompensated and subcompensated void subsamples. The central region of
the distributions ($3$\hMpc\ -- $6$\hMpc), exhibit an approximately flat 
shape, contrary to expected from highly non-linear structures like dark 
matter halos, where the abundances increase for smaller structures. 
The distribution of the FA-T-Web is consistent with a two-barrier problem 
\citep{Sheth04}: formation of large voids is inhibited by the 
\textit{void-in-void} problem (first barrier), where large voids are 
constituted hierarchically of smaller ones. In turn, formation of small 
voids is damped by the \textit{void-in-cloud} problem (second barrier), 
where nearby collapsing structures limit the abundance of embedded small 
voids.

The FA-Vweb scheme does not tackle properly the \textit{void-in-cloud} 
problem as it predicts large abundances of smaller voids. However, an 
interesting result is the difference between the overcompensated and 
subcompensated subsamples. Subcompensated voids, which are expected to 
be embedded in low-density regions like walls and larger voids, exhibit
smaller abundances compatible with the result of the FA-T-Web. Then, the 
most dramatic contribution to the overabundance of small voids for the 
FA-Vweb comes from overcompensated voids. This implies that, although
nearby non-linear structures squeeze out embedded smaller voids, the
rapid and isotropic collapse in these zones, along with the more rugged 
nature of the velocity field make these voids still detectable by this 
scheme.

For both schemes overcompensated voids are more abundant, however at 
larger scales abundances of subcompensated voids become comparable. This 
is somehow expected as larger voids are more likely to abut other voids.
A recent estimation of the radius of the local void gives $r_{LV}\approx
10$ Mpc \citep{Nasonova11}. Taking the dimensionless Hubble constant as 
$h = 0.70$, the size of the local void would be around $\reff = 7$
\hMpc\ in the shown distribution. For both schemes, this places the local
void as a rather common void in terms of size, and more likely to be
overcompensated.

>>>>

We use the Bolshoi simulation to test our void finding method. 
This simulation follows the non-linear evolution of a dark
matter density field on a cubic volume of  size $250$\hMpc\ sampled
with $2048^3$ particles. 
The cosmological parameters in the simulation are $\Omega_{\rm
  m}=0.27$,  $\Omega_{\Lambda}  =0.73$, $h=0.70$, $n=0.95$ and
$\sigma_{8}=0.82$ for the matter density,   cosmological 
constant, dimensionless Hubble parameter, spectral index of
primordial density perturbations and normalization for the power
spectrum, respectively. 
These values are consistent with the ninth year of data of the
Wilkinson  Microwave Anisotropy Probe (WMAP) \citep{Hinshaw2013}. 
For more detailed  technical information about the simulation, see
\citet{Klypin11}.

We use data for the cosmic web identification that is publicly
available through the MultiDark database
\url{http://www.multidark.org/MultiDark/} which is described in
\citet{Riebe11}. 
Here we briefly describe the process to obtain the data. 
For details see \cite{Forero09} (T-Web) and
\cite{Hoffman12,Forero2014} (V-Web). 
This data is based on a  \textit{cloud-in-cell} (\texttt{CIC})
interpolation of the density and velocity fields of the simulation
onto a grid of $256^3$  cells, corresponding to a spatial resolution
of $0.98$\hMpc\ per cell side.    
These fields are smoothed with a gaussian filter with a width of 
$\sigma=0.98$\hMpc. 
The tidal and shear tensors and corresponding eigenvalues are computed
through finite-differences over the potential and velocity fields.

@@

We limit our results to voids with effective radius larger than the
smoothing length of the density field, i.e. $\sim 1$\hMpc.  
Below that scale numerical resolution effects become important. 
With that choice we find a volume filling fraction $54.88\%$ and
$47.06\%$ for the FA-Vweb.

In the following subsections we describe the results for the size
distribution and different radial profiles for all our samples.

@@

Void shapes exhibit a wide range of geometries.
To define their size we use its equivalent spherical radius or
effective radius, defined as $\reff = [3/(4\pi)V]^{1/3}$, with $V$ the 
total volume of the void. 
In Figure \ref{fig:volume_function} we show the void size
distributions for the T-Web and the V-Web.

We see that the void distribution for the T-Web is broadly consistent with the
expectations from a two-barrier problem  \citep{Sheth04}. 
The formation of large voids is limited by the \textit{void-in-void}
problem (first barrier), where large voids are constituted
hierarchically of smaller ones. 
In turn, the formation of small  voids is damped by the
\textit{void-in-cloud} problem (second barrier),  where nearby
collapsing structures limit the abundance of embedded small  voids.

We also find that the V-Web scheme produces an over-abundance of small
voids compared to the resuls of the T-Web.
A large number of these small voids are embedded in dense regions. 
They are visible in the middle panel of Figure \ref{fig:FA_field} as
the small bubbles located inside sheets.
The existence of these small voids could be qualitatively explained by
dynamics of shell crossing in collapsing sheets. 
When matter colides into a sheet, at their center it is possible to
find crossing matter planes that effectively give a possitively
divergen velocity field, which gives a void identification by the
T-Web algorithm. This points has been discussed in \citet{Hoffman12}.

Comparing the abundance of large voids in the two web schemes, we find
that the V-Web is limited to have voids on the scale of $\sim 10$\hMpc,
while the T-Web scheme includes voids as large as $\sim 15$\hMpc. 
Large voids in the T-Web scheme have a velocity structure that
induces a split by the watersched algorithm in the V-Web. 
This is eviden in the right panel of Figure \ref{fig:FA_field}.

%-------------------------------------------------------------------------
\subsection{Compenseated and overcompensated voids}
\label{subsec:enclosedmass}
%-------------------------------------------------------------------------

We find that voids are distributed in two different  families differentiated by the
presence/absence of an overdense matter ridge in their density
profiles. 
To discriminate each void in one of the families we use the
compensation  index $\mathcal{C}$.
It is defined as the mass of a void enclosed in a spherical volume of
radius $R$ and normalized by the mass of the same volume assuming
it is filled by matter with the mean background density.
